---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FunOnFun

<!-- badges: start -->
<!-- badges: end -->

## Purpose

This package does multivariate functional Principal Component Analysis (MFPCA) and then conducts function on function regression the MFPCA scores.

- The URL to the [GitHub](https://github.com/bpar67/FunOnFun)
- The URL to the [Website](https://bpark67.github.io/FunOnFun/)

## Installation

You can install the development version of FunOnFun from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bpark67/FunOnFun")
```

## Dependencies

This package depends on `magrittr`, `dplyr`, `purrr`, `tsibble`, `tibble`, `brolgar`.

## Session Info

This tool was developed using the following R session:

```{r}
devtools::session_info()
```




