---
title: "FunOnFun"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FunOnFun}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FunOnFun)
library(fdapace)
library(tidyverse)
```

# Introduction

Welcome to the `FunOnFun` package! This package is designed to conduct multivariate functional Principal Component Analysis (MFPCA) on irregularly observed data. Let us generate some data:

# Generate Data

## Independence

```{r}
set.seed(16)

n = 20
t = seq(0, 1, length.out = 50)
components = 2

mean_funs = list(
  function(t) -2*(t-0.5)^2 + 5,
  function(t) 3*(t-0.75)^3 - 5
  )

eigen_funs_list = list(
  list(
    function(t) sin(pi*t),
    function(t) cos(pi*t)
  ),
  list(
    function(t) sin(3*pi*t),
    function(t) cos(3*pi*t)
  )
)

lambdas = c(5, 3)

X = FunOnFun::simMFPCA(16, t, n, components, mean_funs, eigen_funs_list, lambdas, response = FALSE)
```

## Dependent

```{r}
mean_funs = list(
  function(t) 6*exp(-(t-1)^2),
  function(t) -2*14^(t-0.5)
)

eigen_funs_list = list(
  list(
    function(t) cos(5*pi*t),
    function(t) sin(5*pi*t)
  ),
  list(
    function(t) sin(3*pi*t),
    function(t) cos(3*pi*t)
  )
)

B = matrix(c(5, 6, 7, 8),
           nrow = components,
           ncol = components)

Y = FunOnFun::simMFPCA(16, t, n, components, mean_funs, eigen_funs_list, lambdas, response = TRUE, B = B)
sigma = 0.001
E = matrix(rnorm(2*length(t)*n, mean = 0, sd = sigma), n, 2*length(t))

Y$X = Y$X + E
```

## Visualize

```{r, out.width = "50%"}
matplot(t(X$X), 
        type='l', 
        ylab='X(t)', 
        xlab='time', 
        main='Plot of predictor curves', 
        col=rgb(0,0,0,alpha=0.4))
matlines(apply(t(X$X), 1, mean),
         type='l',
         lwd=3,
         lty=1,
         col="red")

matplot(t(Y$X), 
        type='l', 
        ylab='Y(t)', 
        xlab='time', 
        main='Plot of response curves', 
        col=rgb(0,0,0,alpha=0.6))
matlines(apply(t(Y$X), 1, mean),
         type='l',
         lwd=3,
         lty=1,
         col = "red")
```

## Simulate Irregular Missingness

```{r}
X_miss = FunOnFun::simMiss(40, X$X, t, seed = 51)
Y_miss = FunOnFun::simMiss(40, Y$X, t, seed = 51)
```

## Visualize Missingness

```{r}
matplot(t(X_miss), 
        type='l', 
        ylab='X(t)', 
        xlab='time', 
        main='Plot of predictor curves with missingness', 
        col=rgb(0,0,0,alpha=0.4))
matlines(apply(t(X_miss), 1, mean, na.rm = T),
         type='l',
         lwd=3,
         lty=1,
         col="red")

matplot(t(Y_miss),
        type='l', 
        ylab='Y(t)', 
        xlab='time', 
        main='Plot of response curves with missingness', 
        col=rgb(0,0,0,alpha=0.6))
matlines(apply(t(Y_miss), 1, mean, na.rm = T),
         type='l',
         lwd=3,
         lty=1,
         col = "red")
```



# MFPCA

```{r}
df = X_miss %>% FunOnFun::tibbleFormat(t) %>% FunOnFun::fpcaFormat(id_col = "id")
df_Y = Y_miss %>% FunOnFun::tibbleFormat(t) %>% FunOnFun::fpcaFormat(id_col = "id")
```

## Get Univariate FPCA Results

```{r}
res_X1 = fdapace::FPCA(df$Variable1,
                       df$Time,
                       list(dataType = "Sparse",
                            error = F,
                            kernel = "epan",
                            verbose = F,
                            nRegGrid = length(t)))

res_X2 = fdapace::FPCA(df$Variable2,
                       df$Time,
                       list(dataType = "Sparse",
                            error = F,
                            kernel = "epan",
                            verbose = F,
                            nRegGrid = length(t)))

res_Y1 = fdapace::FPCA(df_Y$Variable1,
                       df_Y$Time,
                       list(dataType = "Sparse",
                            error = T,
                            kernel = "epan",
                            verbose = F,
                            nRegGrid = length(t),
                            methodSelectK = 2))
res_Y2 = fdapace::FPCA(df_Y$Variable2,
                       df_Y$Time,
                       list(dataType = "Sparse",
                            error = T,
                            kernel = "epan",
                            verbose = F,
                            nRegGrid = length(t),
                            methodSelectK = 2))
```

## Run Irregular MFPCA

```{r}
res = FunOnFun::irregMFPCA(components = 2,
                           split = T,
                           res_X1,
                           res_X2)

res_Y = FunOnFun::irregMFPCA(components = 2,
                             split = T,
                             res_Y1,
                             res_Y2)
```









